Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-26 paper.tex
Added a screenshot for the BOx website

@@

One recent development
that attempts to address this issue was the establishment in Apr 2010 of a
question-and-answer
website related to Blue Obelisk projects and themes at
http://blueobelisk.shapado.com. This is a website in the
style of Stack Overflow that encourages high quality answers (and
questions) through the use of a voting system. In the year since it
was established, over
200 users have registered, many of whom had no previous involvement
with the Blue Obelisk.

@@

>>>>

\subsection*{Getting the message out}

One recent development
that attempts to address this issue was the establishment in Apr 2010 of a
question-and-answer (QA)
website related to Blue Obelisk projects and themes at
http://blueobelisk.shapado.com (see Figure~3). This is a website in the
style of Stack Overflow that encourages high quality answers (and
questions) through the use of a voting system. In the year since it
was established, over
200 users have registered, many of whom had no previous involvement
with the Blue Obelisk, showing that the QA website is a nice complement
to earlier existing channels of communication.

@@

@@

  \subsection*{Figure 3 - Screenshot of the Blue Obelisk eXchange Question
    and Answer website.}
